%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Co-founder \& Software Engineer} % Job title
    {What to do} % Organization
    {Salford, Greater Manchester} % Location
    {Jun. 2016 - PRESENT} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Implementing a backend with Java, Spring, Hibernate for a React frontend.}
            \item {Collaborating remotely with other developers in our spare time.}
            \item {Given me experience in attending regular meetings as well as show me the structure of a small development team.}
            \item {2 members of this team do not have technical skills, therefore I've had to work on communicating complex concepts in simpler terms.}
        \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Freelance} % Job title
    {Rise Universal Developments} % Organization
    {Glossop, Derbyshire} % Location
    {Apr. 2016 - Aug. 2016} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Developed a reserve and collect web application for a local building \& joinery company.}
            \item {Technologies used included Java, Spring, SQL, HTML5, CSS3, JS.}
            \item {Gained experience dealing with clients. i.e. meetings, forming requirements and negotiating payment.}
            \item {Gained vital experience in understanding the timing and scale of projects, in addition to improving my time management skills when meeting deadlines.}
        \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
