%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Member} % Affiliation/role
    {Salford Computing Society} % Organization/group
    {University of Salford} % Location
    {Sept. 2015 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Being a part of the society has given me the opportunity to deliver talks and presentations to a group of peers.}
        \item {Took part in regular programming challenges.}
        \item {Mentored both first and second year students in Java as a part of a society organised program. I helped by supporting and guiding them in the right direction when needed.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Participant} % Affiliation/role
    {Hack Manchester} % Organization/group
    {Manchester Museum of Science \& Industry} % Location
    {29 Oct. 2016 - 30 Oct. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Built a tablet based in-store app for the Co-op challenge. }
        \item {Technologies used include Java, Spring, MySQL.}
        \item {Had the opportunity to practice using Git for collaboration on the back-end.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Participant} % Affiliation/role
    {Great Uni Hack} % Organization/group
    {Manchester Metropolitan University} % Location
    {12 Nov. 2016 - 13 Nov. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Won the HackHarassment challenge. Built HarassBlock, a harassment blocking browser extension inspired by Ad-Block.}
        \item {Wrote a NLP (Natural Language Processing) module in Python, a language that I had never used.}
        \item {I was able to apply my knowledge of other languages and general programming principles to get the module done.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Student} % Affiliation/role
    {International Cyber Security Summer Camp} % Organization/group
    {Amsterdam University of Applied Sciences} % Location
    {29 Aug. 2016 - 2 Sept. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Learned from industry leading experts and gained practical experience in offensive security, reverse engineering, malware analysis, threat intelligence, forensics and exploit development.}
        \item {Underwent a team-based realistic 12-hour simulation scenario saving Amsterdam from a terrorist attack.}
        \item {During this period we demonstrated forensic analysis of an sd card, uncovering data hidden with stegonography, colliding hashes, reverse engineering communication programs, ending in a hunt for the final evidence around Amsterdam.}
        \item {Gained great experience working in teams of 10. Students were from the UK, Netherlands, France and Croatia. Everyone contributed a variety of different skill sets which allowed us to work effectively as a team.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Participant} % Affiliation/role
    {Hack Manchester} % Organization/group
    {Manchester Museum of Science \& Industry} % Location
    {24 Oct. 2015 - 25 Oct. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Built an Android application used to battle monsters that appear based on proximity to Bluetooth beacons.}
        \item {Gained better understanding of the Android SDK, SQLite as well as communicating with external services via JSON.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Participant} % Affiliation/role
    {Great Uni Hack} % Organization/group
    {Manchester Metropolitan University} % Location
    {31 Oct. 2015 - 1 Nov. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Built an application for clients of an unmanaged public work space as part of the Rise challenge.}
        \item {I implemented an Android application which communicated with a node backend using WebSockets.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Volunteer Mentor} % Affiliation/role
    {Yound Rewired State - Festival of Code} % Organization/group
    {Barclays Bank, Manchester Offices} % Location
    {25 Jul. 2015 - 2 Aug. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Mentored a group of 4-6 children under the age of 18, ranging from 8 to 16 during a week long hackathon.}
        \item {Provided support as they developed an Android application connected to Google APIs.}
        \item {Application was using Google's speech to text in order to transcribe conversations and communicate with deaf individuals without the need for sign language.}
        \item {I was inspired to do this as I never had a mentor or anyone who I could guide me when I was learning to code as a teenager.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
